Block bootstrap consistency\\under weak assumptions

### 2015-12-31 Paper.tex

First, the relevant probability infrastructure.  Let
$(S, \Omega, \pr)$ be a probability space and define the sequence of
sub-sigma-fields $\Omega_n \subset \Omega$. Assume that each
$X_{nt}$, $V_{nt}$, $M_{nj}$, and $u_{nj}$ is $\Omega_n$-measurable,
with $u_{nj}$ the $\operatorname{uniform}(1,\dots,n)$ random variables
that designate the start period of each bootstrap ``block.'' Also
define the \sigmafield\ generated by the stationary bootstrap's block
lengths alone, which will be used repeatedly in our results,
\begin{equation}
  \Ms = \sigma(J_{n}, M_{n1},\dots,M_{nJ_n})
\end{equation}
and the conditional probability $\Pm(\cdot) = \pr[\cdot \mid \Ms]$.
(And define $\Pm^*(\cdot) = \pr^*[\cdot \mid \Ms]$, $\Em(\cdot) =
\E^*(\cdot \mid \Ms)$, etc.) An important property is
that $\Ms$ is \emph{independent} of the $X_{nt}$'s, $V_{nt}$'s, and
$u_{nj}$'s, so we can treat any
$M_{nj}$ and $J_n$ terms as constants within $\Em(\cdot)$ and
$\Pm[\cdot]$ and integrate over the unconditional distributions of the
other random variables. This property is especially important because it allows us
to use maximal inequalities and other moment inequalities for
mixingale arrays with only small modifications to construct almost sure bounds on the
conditional moments $\Em$.

@@

\begin{lem}\label{equivalent-convergence-from-lie-lemma}
  If $\{A_n\}$ is a sequence of events in $\Omega$ then the following
  are equivalent:
  \begin{align*}
  \pr[A_n] &\to 0, &
  \pr^*[A_n] &\to 0 \text{\ in\ }L_1, &
  &\text{and}&
  \Pm^*[A_n] &\to 0 \text{\ in\ }L_1.
  \end{align*}
\end{lem}
\begin{proof}
  Since $|\pr[A_n]| = \E |\pr^*[A_n]| = \E |\pr^*_{\mathcal{M}}[A_n]|$ these
  conditions are equivalent by definition.
\end{proof}

>>>>

Define the \sigmafield
\begin{equation}
  \Ms = \sigma(J_{n}, M_{n1},\dots,M_{nJ_n})
\end{equation}
and the conditional probability $\Pm(\cdot) = \pr[\cdot \mid \Ms]$.
(And define $\Pm^*(\cdot) = \pr^*[\cdot \mid \Ms]$, $\Em(\cdot) =
\E^*(\cdot \mid \Ms)$, etc.) An important property is
that $\Ms$ is \emph{independent} of the $X_{nt}$, so we can treat any
$M_{nj}$ and $J_n$ terms as constants within $\Em(\cdot)$ and
$\Pm[\cdot]$ and integrate over the unconditional distributions of the
$X_{nt}$. This property is especially important because it allows us
to use maximal inequalities and other moment inequalities for
mixingale arrays without modification to construct almost sure bounds on the
conditional moments $\Em$.

@@

\begin{lem}\label{equivalent-convergence-from-lie-lemma}
  If $\{A_n\}$ is a sequence of events then the following are equivalent:
  \begin{align*}
  \pr[A_n] &\to 0, &
  \pr^*[A_n] &\to 0 \text{\ in\ }L_1, &
  &\text{and}&
  \Pm^*[A_n] &\to 0 \text{\ in\ }L_1.
  \end{align*}
\end{lem}
\begin{proof}
  Since $|\pr[A_n]| = \E |\pr^*[A_n]| = \E |\pr^*_{\mathcal{M}}[A_n]|$ these
  conditions are equivalent by definition.
\end{proof}

### 2015-12-31 subs/ETr2/reply_3.tex

@@

\end{enumerate}
\end{document}

>>>>

  The aim of the paper is to relax the conditions required by
  \cite{GoW:02} and \cite{GoJ:03}. A major focus of \cite{GoW:02} is
  proving consistency of these block bootstraps under some degree of
  heterogeneity in the means\,---\,one example is, as they put it, ``a
  finite number of properly behaved breaks in means.'' For our results
  to be comparable to theirs in this way, even to show that we do not
  allow as much heterogeneity in the means as those papers do, it's
  important that we use array notation. So, an example where array
  notation is important in applciations is when there is a break in
  the mean at observation $n/2$.

  While I agree with what you wrote in the previous letter, ``it is
  never a good practice to copy what other authors do, as an
  alternative to justifying it,'' I also think that readers generally
  benefit when authors reuse decent notation from other closely
  related papers, even if a different notation is incrementally
  better.

  Another question raised in your previous letter was: why explicitly
  normalize by $1/\sqrt{n}$ and why take means? As mentioned in the
  previous paragraph, each $X_{nt}$ is allowed to have nonzero mean,
  so estimates of the variance need to be explicitly demeaned. Making
  the normalization explicit makes these operations transparent. Once
  the series is demeaned (either using the sample mean or the
  population mean), all of the mathematics uses the various $Z_{nj}$
  terms which have an implicit normalization.

  In any case, I have added an explanation for these choices as
  Footnote 6 in the paper.

@@

\end{enumerate}

\bibliography{../../texextra/references}
\end{document}
